The Role of Shallow Processing in Agreement Attraction

### 2019-12-23 agremeent_draft_dec17/draft_dec17.Rnw
rnw done I guess

\documentclass[a4paper,man,natbib]{apa6}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

\title{The Role of Shallow Processing in Agreement Attraction}
\shorttitle{Your APA6-Style Manuscript}
\author{Utku Türk, Pavel Loga\v{c}ev}
\affiliation{Boğaziçi University}

\abstract{We report the results of two speeded acceptability judgment experiments in Turkish. We hypothesized an alternative explanation for agreement attraction effects in Turkish that is based on shallow processing. Our findings contradict our hypothesized form-driven processing strategy and support an account of agreement attraction based on the use of abstract linguistic features, rather than mere form.}
\input{settings.tex}
\begin{document}
\maketitle

@@

\section{Experiment 1} \label{sec:exp1}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/exp1AvgResponse-1.png}
\caption{Percentage of ‘yes’ (acceptable) responses of Experiment 1 and \citet{LagoEtAl:2018}}
\label{fig:exp1AvgResponse}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/exp1ResponseModelPlot-1.png}
\caption{Estimates and 95\% credible intervals for the regression coefficients for Experiment 1}
% give details regarding encoding etc.
\label{fig:exp1ResponseModel}
\end{figure}

@@

@@

\autoref{fig:exp2AvgResponse} shows the average proportions of 'acceptable' responses by experimental conditions for both Experiment 1 and Experiment 2. We see that there is no effect resembling agreement attraction in the ungrammatical conditions of Experiment 2. Ungrammatical conditions showed comparable effects (X, Y) regardless of the attractor's number.  
\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/exp2AvgResponse-1.png}
\caption{Estimates and 95\% credible intervals for the regression coefficients for Experiment 1 and Experiment 2}
% give details regarding encoding etc.
\label{fig:exp2AvgResponse}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/exp2ResponseModelPlot-1.png}
\caption{Estimates and 95\% credible intervals for the regression coefficients for Experiment 2}
% give details regarding encoding etc.
% similar to experiment1 model graph 
\label{fig:exp2ResponseModel}
\end{figure}

>>>>

\documentclass[doc,a4paper,man,natbib,floatsintext,noextraspace]{apa6}
<<echo=F>>=
# Set the global chunk options
set.seed(42)
knitr::opts_chunk$set(encoding = 'UTF-8',
                      cache.extra = knitr::rand_seed,
                      echo = F,
                      results = 'hide',
                      message = F,
                      warning = F)
options("citation_format" = "pandoc")
@
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[singlespacing]{setspace}
<<>>=
# load packages
library(knitcitations)
library(car, warn.conflicts = FALSE)
library(MASS)
library(brms)
library(xtable)
library(ggpubr)
library(languageR)
library(tidyverse)
library(gdata)
library(magrittr)
library(ggplot2)
theme_set(theme_bw())

source("../scripts/misc.R")

@
\title{The Role of Shallow Processing in Agreement Attraction}
\shorttitle{Your APA6-Style Manuscript}
\author{Utku Türk, Pavel Loga\v{c}ev}
\affiliation{Boğaziçi University}

\abstract{We report the results of two speeded acceptability judgment experiments in Turkish. We hypothesized an alternative explanation for agreement attraction effects in Turkish that is based on shallow processing. Our findings contradict our hypothesized form-driven processing strategy and support an account of agreement attraction based on the use of abstract linguistic features, rather than mere form.}
\input{settings.tex}
\begin{document}

\maketitle

@@

\section{Experiment 1} \label{sec:exp1}
% do not do this in one chunk. differentiate the chunks and give them proper names.
<<>>=
fname_data <- "../workspace_exp1/exp_data.rds"
data_exp1 <- readRDS(file = fname_data)

### note: the low accuracy on fillers is not caused by a couple of items
# filler_avgs <- 
# data_exp1 %>% subset(Type == "filler") %>% group_by(Item, condition) %>% 
#               summarize(M = mean(ResponseYes, na.rm = T)) %>%
#               arrange(condition, Item)
# fillers %>% subset(condition == "a") 
# fillers %>% subset(condition == "b")
###

# compute by-subject percentages of 'yes' responses, and average RTs 
avg_by_subj <- data_exp1 %>%
                group_by(subject, experiment, condition, 
                         grammatical, verb_num, attractor_num) %>%
                summarize(avRT = mean(RT), 
                          p_yes = mean(ResponseYes, na.rm = T), 
                          N = sum(!is.na(ResponseYes))  )

# reformat by-subject averages to a wide format
avg_by_subj_wide <- avg_by_subj %>% 
                      mutate(expcond = paste(experiment, condition, sep="_")) %>% 
                      ungroup() %>%
                      dplyr::select(-experiment, -condition, -avRT, -N,
                                    -grammatical, -verb_num, -attractor_num) %>%
                      tidyr::spread(expcond, p_yes) %>% 
                      mutate(delta_dc = AgrAttr_d - AgrAttr_c)

# Load Lago et al.'s monolingual data
fname_lagoetal <- "../Data/Lago_et_al/Lago_data.csv"
df_lagoetal <- read.csv(fname_lagoetal, encoding = "UTF-8", as.is = T)
df_lagoetal %<>% subset(Group == "monolingual")
df_lagoetal %<>% dplyr::select(-Accuracy, -L1:-Group, -List:-SelfRateGerman)

# Note: All rows with Experiment == "offline" also seem to be for 
#       the UNP task ('Grammatical' is NA). I wonder if these were
#       the same subjects, or if the subject labels were simply the same
#       for the two experiments.
with(df_lagoetal, stopifnot( is.na(Grammatical) == (Experiment == "offline") ))

df_lagoetal_unp <- df_lagoetal %>% 
                    subset(is.na(Grammatical)) %>%
                    dplyr::select(-Grammatical:-Label)
df_lagoetal_attr <- df_lagoetal %>% 
                  subset(!is.na(Grammatical)) %>%
                  dplyr::select(-Distance:-NewCond)

df_lagoetal_attr %<>% mutate(ResponseYes = (Response == "yes") ) %>% 
                      dplyr::select(-Response)
df_lagoetal_attr %<>% ungroup() %>%
                      dplyr::select(grammatical=Grammatical,
                                    attractor_num=Attractor,
                                    experiment=Experiment,
                                    lagoetal_condition=Condition, 
                                    subject=Participant, 
                                    item=Item,
                                    ResponseYes,
                                    RT)

# map to our condition labels
lagoetal_condition_mapping <- data.frame(
    condition = c("a", "b", "c", "d"),
    lagoetal_condition = c("d", "b", "c", "a"), 
    stringsAsFactors = F)

df_lagoetal_attr %<>% left_join( lagoetal_condition_mapping, by = "lagoetal_condition" )

# compute by-subject percentages of 'yes' responses, and average RTs 
avg_by_subj_lagoetal <- df_lagoetal_attr %>%
            group_by(subject, experiment, condition, grammatical, attractor_num) %>%
            summarize(avRT = mean(RT), 
                      p_yes = mean(ResponseYes, na.rm = T), 
                      N = sum(!is.na(ResponseYes))  )

# reformat by-subject averages to a wide format
avg_by_subj_lagoetal_wide <- avg_by_subj_lagoetal %>% 
            mutate(expcond = paste(experiment, condition, sep="_")) %>% 
            ungroup() %>%
            dplyr::select(-experiment, -condition, -avRT, -N,
                          -grammatical, -attractor_num) %>%
            tidyr::spread(expcond, p_yes) %>% 
            mutate(delta_dc = online_d - online_c)
word_freq <- readxl::read_excel("../Data/freq.xlsx", sheet = 1)
word_freq$freq_percentage %<>% as.numeric()
word_freq %<>% dplyr::select(-freq_standardized, -freq_percentage, -word)
word_freq %<>% tidyr::spread(place, freq_count)

word_freq %<>% dplyr::group_by(exp) %>% 
               dplyr::mutate( cat_n1 = ifelse(n1 > median(n1), "high", "low"),
                              cat_n2 = ifelse(n2 > median(n2), "high", "low"),
                              freqlog_n1 = scale(log(n1)),
                              freqlog_n2 = scale(log(n2)),
                              freqlog_n1n2 = log(n1) - log(n2)
                            ) %>% 
                ungroup()
word_freq$cat_n1 %<>% as.factor()
word_freq$cat_n2 %<>% as.factor()

word_freq_exp1 <- word_freq %>% 
                    subset(exp == "up") %>% 
                    dplyr::select(-exp)
word_freq_lago <- word_freq %>% 
                    subset(exp == "lago") %>% 
                    dplyr::select(-exp)

# identify bad participants 
bad_subjects <- subset(avg_by_subj_wide, delta_dc <= 0.25 ) %>% .$subject
data_exp1_clean <- data_exp1 %>% subset(!subject %in% bad_subjects)

# identify bad participants 
bad_subjects_lagoetal <- subset(avg_by_subj_lagoetal_wide, delta_dc <= 0.25 ) %>% .$subject
df_lagoetal_attr_clean <- df_lagoetal_attr %>% subset(!subject %in% bad_subjects_lagoetal)
df_merge_exp1 <- data_exp1_clean %>% ungroup() %>% 
                      dplyr::select(source=experiment, 
                                    grammatical, attractor_num,
                                    # condition,
                                    subject, item=Item,
                                    ResponseYes, RT)
df_merge_exp1$experiment <- "Experiment 1"
df_merge_exp1$grammatical <- with(df_merge_exp1, 
                                  ifelse(grammatical == "gram", 
                                          "grammatical",
                                          "ungrammatical"))
df_merge_exp1$attractor_num <- with(df_merge_exp1, 
                                    ifelse(attractor_num == "pl",
                                           "plural", 
                                           "singular"))
df_merge_exp1$item %<>% as.integer()
df_merge_exp1$subject %<>% as.character()
#df_merge_exp1 %<>% left_join(word_freq_exp1, by = "item")

df_merge_lago <- df_lagoetal_attr_clean %>%
                      ungroup() %>% 
                      dplyr::select(grammatical, attractor_num,
                                    subject, item, ResponseYes, RT)
#df_merge_lago %<>% left_join(word_freq_lago, by = "item")
df_merge_lago$experiment <- "Lago et al. (2018)" 
df_merge_lago$source <- NA
df_merge_lago$item %<>% add(1000)

df_merged <- dplyr::bind_rows(df_merge_exp1, df_merge_lago)
df_merged$subject %<>% as.factor()
df_merged$item %<>% as.factor()

df_exp1_na_nofillers <- subset(df_merge_exp1, is.na(ResponseYes) & source != "filler")
df_merged %<>% subset( !is.na(ResponseYes) )

@

@@

<<exp1AvgResponse, fig.cap='Percentage of \\emph{yes} (acceptable) responses of Experiment 1 and \\citet{LagoEtAl:2018}', fig.height=3, fig.align='center'>>=

df_merged %<>% mutate(ResponseCorrect = (ResponseYes == (grammatical == "grammatical") ) )
df_merged_nonna <- df_merged %>% subset(!is.na(ResponseYes))

# avg_clean <- 
# df_merged %>% subset(experiment == "Lago et al. (2018)") %>%
#      group_by(experiment, source, grammatical, attractor_num, subject) %>%
#      summarize(p_yes = mean(ResponseYes, na.rm=T)) %>%
#      summarize(p_yes = mean(p_yes))

avg_clean <- list()
avg_clean$resp <- df_merged_nonna %>% 
              plyr::ddply(c("experiment"), function(df) {
              df %>% se_cousineau(n_conditions = 4, subject, DV = ResponseYes, 
                           group = c("experiment", "source", "grammatical", "attractor_num"), 
                           is_proportion = TRUE)
})

avg_clean$rt <- df_merged_nonna %>%
              plyr::ddply(c("experiment"), function(df) {
              df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
                           group = c("experiment", "source", "grammatical", "attractor_num"), 
                           is_proportion = FALSE)
})

avg_clean$rt_correct <- df_merged_nonna %>% subset(ResponseCorrect) %>%
              plyr::ddply(c("experiment"), function(df) {
              df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
                           group = c("experiment", "source", "grammatical", "attractor_num"), 
                           is_proportion = FALSE)
})

avg_exp <- avg_clean %>% lapply(function(df) { df %>% subset(is.na(source) | source != "filler") })
avg_fillers <- avg_clean %>% lapply(function(df) { df %>% subset(source == "filler") })

p_avg_resp <- avg_exp$resp %>%
              ggplot(aes(grammatical, M, #linetype = attractor_num, 
                         color = attractor_num, group = attractor_num)) + 
                geom_point() + geom_line() + 
                facet_wrap(~experiment)

p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1)

# p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
#                             geom_point(data = avg_fillers) +

p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) +
                           theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent)#, breaks = c(0, .25, .5, .75, 1))
p_avg_resp <- p_avg_resp + theme_bw()
p_avg_resp <- p_avg_resp + scale_color_discrete(name = "Attractor Number")
print(p_avg_resp)

if (exists("le_poster")) {
  p_avg_resp <- avg_exp$resp %>% subset(experiment == "Experiment 1") %>%
                ggplot(aes(grammatical, M, #linetype = attractor_num, 
                           color = attractor_num, group = attractor_num)) + 
                  geom_point() + geom_line() + theme( strip.background = element_rect(fill="white")) +
                  facet_wrap(~experiment)

  p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1)

  # p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
  #                             geom_point(data = avg_fillers) +

  p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) +
                             theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
  p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent, limits = c(0,1))#, breaks = c(0, .25, .5, .75, 1))
  p_avg_resp <- p_avg_resp + theme_bw()
  p_avg_resp <- p_avg_resp + scale_color_discrete(name = "Attractor Number")
  ggsave(filename = "./plots_le/exp1.jpeg", p_avg_resp, height = 2.5, width = 2.5*2)
}

@

@@

<<>>=

df_merged %<>% within(., {
  cGrammatical <- ifelse(grammatical == "grammatical", .5, -.5)
  cUngrammatical <- ifelse(grammatical == "ungrammatical", .5, -.5)
  cAttractorPlural <- ifelse(attractor_num == "plural", .5, -.5)
  cEndsInConsonant <- ifelse(experiment != "Experiment 1", .5, -.5)
  #cFreqlog_n1n2 <- scale(freqlog_n1n2)
  #cFreqlog_n1 <- scale(freqlog_n1)
  #cFreqlog_n2 <- scale(freqlog_n2)
})
df_merged_nofillers <- df_merged %>% subset(is.na(source) | source != "filler")

# ## test model parameterization using a simple GLM first
# m <- glm(ResponseYes ~ (cFreqlog_n1 + cFreqlog_n2) *
#            cEndsInConsonant * cUngrammatical * cAttractorPlural,
#          data = df_merged_nofillers,
#          family = binomial("probit"))
# summary(m)

n_chains <- 4
n_cores <- 4
n_iter <- 2000

fname_exp1_responses <- "../workspace_exp1/model_responses"
m_responses <- brm(ResponseYes ~ cEndsInConsonant * cUngrammatical * cAttractorPlural + 
                                 (cUngrammatical * cAttractorPlural + 1| subject) +
                                 (cUngrammatical * cAttractorPlural + 1| item),
                   data = df_merged_nofillers,
                   family = bernoulli("probit"),
                   file = fname_exp1_responses, 
                   chains = n_chains, cores = n_cores, iter = n_iter)

fname_exp1_responses_minimal <- "../workspace_exp1/model_responses_minimal"
m_responses_minimal <- brm(ResponseYes ~ (cEndsInConsonant + cUngrammatical + cAttractorPlural)^2 + 
                                         (cUngrammatical * cAttractorPlural + 1| subject) +
                                         (cUngrammatical * cAttractorPlural + 1| item),
                   data = df_merged_nofillers,
                   family = bernoulli("probit"),
                   file = fname_exp1_responses_minimal, 
                   chains = n_chains, cores = n_cores, iter = n_iter)

fname_exp1_rts <- "../workspace_exp1/model_responses_rt"
m_rts <- brm(RT ~ cEndsInConsonant * cUngrammatical * cAttractorPlural +
                                 (cUngrammatical * cAttractorPlural + 1| subject) +
                                 (cUngrammatical * cAttractorPlural + 1| item),
                   data = df_merged_nofillers,
                   family = lognormal(),
                   file = fname_exp1_rts,
                   chains = n_chains, cores = n_cores, iter = n_iter)

if (exists("le_poster"))
{
  fname_exp1_responses <- "../workspace_exp1/model_responses_justexp1"
  m_responses_exp1 <- brm(ResponseYes ~ cUngrammatical * cAttractorPlural + 
                                 (cUngrammatical * cAttractorPlural + 1| subject) +
                                 (cUngrammatical * cAttractorPlural + 1| item),
                   data = df_merged_nofillers %>% subset(experiment == "Experiment 1"),
                   family = bernoulli("probit"),
                   file = fname_exp1_responses, 
                   chains = n_chains, cores = n_cores, iter = n_iter)

}

@

<<exp1ResponseModel, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Experiment 1', fig.height=3, fig.align='center'>>=
contrast_names <- c("cUngrammatical" = "Ungrammaticality",
                    "cAttractorPlural" = "Plural Attactor",
                    "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
                    "cEndsInConsonant" = "Ambiguity",
                    "cEndsInConsonant:cUngrammatical" = "Ambiguity * Ungrammaticality",
                    "cEndsInConsonant:cAttractorPlural" = "Ambiguity * Plural Attractor",
                    "cEndsInConsonant:cUngrammatical:cAttractorPlural" = "Ambiguity * Ungrammaticality * Plural Attractor")

p_m_response <- 
  create_model_coefs_plot( m_responses, 
        plot_stats = T, map_names = contrast_names,
        expand_right = 2.5, expand_top = 2, x_stat_adjust = 1.1,
        x_breaks = c(-3,-2,-1, 0,1, 2) ) + 
        xlab("Estimate (log-odds)")

suppressWarnings({
print(p_m_response + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment"))
})

if (exists("le_poster"))
{
    p_m_response_exp1 <- 
      create_model_coefs_plot( m_responses_exp1, 
            plot_stats = T, map_names = contrast_names,
            expand_right = 2.5, expand_top = 5, x_stat_adjust = 1.1,
            x_breaks = c(-3,-2,-1, 0,1, 2) ) + 
            xlab("Estimate (log-odds)")

    p_m_response_exp1 <- p_m_response_exp1 + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment")

    ggsave(filename = "./plots_le/m_exp1.jpeg", p_m_response_exp1, height = 1.5, width = 2.5*2)
}
@

@@

<<loadExperiment2Data>>=
fname_data2 <- "../workspace_exp2/exp_data.rds"
data_exp2 <- readRDS(file = fname_data2)

# compute by-subject percentages of 'yes' responses, and average RTs 
avg_by_subj2 <- data_exp2 %>%
                group_by(subject, experiment, condition, 
                         grammatical, verb_num, attractor_num) %>%
                summarize(avRT = mean(RT), 
                          p_yes = mean(ResponseYes, na.rm = T), 
                          N = sum(!is.na(ResponseYes))  )

# reformat by-subject averages to a wide format
avg_by_subj_wide2 <- avg_by_subj2 %>% 
                      mutate(expcond = paste(experiment, condition, sep="_")) %>% 
                      ungroup() %>%
                      dplyr::select(-experiment, -condition, -avRT, -N,
                                    -grammatical, -verb_num, -attractor_num) %>%
                      tidyr::spread(expcond, p_yes) %>% 
                      mutate(delta_dc = AgrAttr_d - AgrAttr_c)

@

<<badSubjects2>>=
# identify participants 
bad_subjects2 <- subset(avg_by_subj_wide2, delta_dc <= 0.25 ) %>% .$subject

data_exp2_clean <- data_exp2 %>% subset(!subject %in% bad_subjects)

@

<<mergeData2>>=

df_merge_exp2 <- data_exp2_clean %>% ungroup() %>% 
                      dplyr::select(source=experiment, grammatical, attractor_num, # condition,
                                    subject, item=Item,
                                    ResponseYes, RT)
df_merge_exp2$experiment <- "Experiment 2"
df_merge_exp2$grammatical <- with(df_merge_exp2, ifelse(grammatical == "gram", 
                                                        "grammatical",
                                                        "ungrammatical"))
df_merge_exp2$attractor_num <- with(df_merge_exp2, ifelse(attractor_num == "pl", 
                                                          "plural", 
                                                          "singular"))
df_merge_exp2$item %<>% as.integer()
df_merge_exp2$subject %<>% as.character()

df_exp2_na_nofillers <- subset(df_merge_exp2, is.na(ResponseYes))

df_merged2 <- dplyr::bind_rows(df_merge_exp1, df_merge_exp2)
df_merged2$subject %<>% as.factor()
df_merged2$item %<>% as.factor()

df_merged2_nonna <- df_merged2 %>% subset(!is.na(ResponseYes))
@

<<computeAverages2>>=

# avg_clean2 <- df_merged2 %>%
#                 group_by(experiment, source, grammatical, attractor_num) %>%
#                 summarize(avgRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T))
# # XXX

avg_clean2 <- list()
avg_clean2$resp <- df_merged2_nonna %>% 
              plyr::ddply(c("experiment"), function(df) {
              df %>% se_cousineau(n_conditions = 4, subject, DV = ResponseYes, 
                           group = c("experiment", "source", "grammatical", "attractor_num"), 
                           is_proportion = TRUE)
})

avg_clean2$rt <- df_merged2_nonna %>%
              plyr::ddply(c("experiment"), function(df) {
              df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
                           group = c("experiment", "source", "grammatical", "attractor_num"), 
                           is_proportion = FALSE)
})

# TODO: Code ResponseCorrect and re-enable
# avg_clean$rt_correct <- df_merged2_nonna %>% subset(ResponseCorrect) %>%
#               plyr::ddply(c("experiment"), function(df) {
#               df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
#                            group = c("experiment", "source", "grammatical", "attractor_num"), 
#                            is_proportion = FALSE)
# })

avg_exp2 <- avg_clean2 %>% lapply(function(df) { df %>% subset(is.na(source) | source != "filler") })
#avg_fillers <- avg_clean %>% lapply(function(df) { df %>% subset(source == "filler") })

@

@@

\autoref{fig:exp2AvgResponse} shows the average proportions of 'acceptable' responses by experimental conditions for both Experiment 1 and Experiment 2. We see that there is no effect resembling agreement attraction in the ungrammatical conditions of Experiment 2. Ungrammatical conditions showed comparable effects (X, Y) regardless of the attractor's number.

<<exp2AvgResponse, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Experiment 1 and Experiment 2', fig.height=3, fig.align='center'>>=

avg_exp2 <- avg_clean2$resp %>% subset(is.na(source) | source != "filler") %>% subset(experiment == "Experiment 2")
avg_fillers2 <- avg_clean2$resp %>% subset(source == "filler") %>% subset(experiment == "Experiment 2")

p_avg_resp2 <- ggplot(avg_exp2, aes(grammatical, M, #linetype = attractor_num, 
                                    color = attractor_num, group = attractor_num)) + 
                geom_point() + geom_line() + 
                facet_wrap(~experiment) +
                theme_bw() + theme( strip.background = element_rect(fill="white") ) +
                xlab("") + ylab("Percentage 'acceptable'")

p_avg_resp2 <- p_avg_resp2 + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1)
p_avg_resp2 <- p_avg_resp2 + scale_y_continuous(labels=scales::percent)
p_avg_resp2 <- p_avg_resp2 + scale_color_discrete(name = "Attractor Number")

print(p_avg_resp2)

if (exists("le_poster")) {

  p_avg_resp2 <- p_avg_resp2 + scale_y_continuous(labels=scales::percent, limits = c(0, 1))
  ggsave(filename = "./plots_le/exp2.jpeg", p_avg_resp2, height = 2.5, width = 2.5*2)
}

@

@@

<<Model>>=

# to-do: Rename 'cVerbalPlural' to 'cVerbalAttractor'
df_merged2 %<>% within(., {
  cGrammatical <- ifelse(grammatical == "grammatical", .5, -.5)
  cUngrammatical <- ifelse(grammatical == "ungrammatical", .5, -.5)
  cAttractorPlural <- ifelse(attractor_num == "plural", .5, -.5)
  cVerbalPlural <- ifelse(experiment == "Experiment 2", .5, -.5)
})
df_merged_nofillers2 <- df_merged2 %>% subset(is.na(source) | source != "filler")

# ## test model parameterization using a simple GLM first
# m <- glm(ResponseYes ~ cEndsInConsonant * cUngrammatical * cAttractorPlural,
#          data = df_merged_nofillers,
#          family = binomial("probit"))
# summary(m)

n_chains <- 4
n_cores <- 4
n_iter <- 2000

fname_exp2_responses <- "../workspace_exp2/model_responses"

library(brms)

m_responses2 <- brm(ResponseYes ~ cVerbalPlural * cUngrammatical * cAttractorPlural + 
                                 (cUngrammatical * cAttractorPlural + 1| subject) +
                                 (cUngrammatical * cAttractorPlural + 1| item),
                   data = df_merged_nofillers2,
                   family = bernoulli("probit"),
                   file = fname_exp2_responses, 
                   chains = n_chains, cores = n_cores, iter = n_iter)

@

<<exp2ResponseModel, fig.cap='Estimates and 95\\% credible intervals for the regression coefficients for Experiment 2', fig.height=3, fig.align='center'>>=

contrast_names2 <- c("cUngrammatical" = "Ungrammaticality",
                    "cAttractorPlural" = "Plural Attactor",
                    "cVerbalPlural" = "Verbal Attractor",
                    "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
                    "cVerbalPlural:cUngrammatical" = "Ungrammaticality * Verbal Attractor",
                    "cVerbalPlural:cAttractorPlural" = "Verbal Attractor * Plural Attractor",
                    "cVerbalPlural:cUngrammatical:cAttractorPlural" = "Verbal Attractor * Ungrammaticality * Plural Attractor")

p_m_response2 <- create_model_coefs_plot(m_responses2, map_names = contrast_names2)
p_m_response2 <- p_m_response2 + xlab("Estimate (log-odds)")
print(p_m_response2 + annotate(x=-2, xend=2, y=0, yend=0, lwd=0.25, geom="segment"))

if (exists("le_poster"))
{
contrast_names2_le <- c("cUngrammatical" = "Ungrammaticality",
                    "cAttractorPlural" = "Plural Attactor",
                    "cVerbalPlural" = "Verbal Attractor",
                    "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
                    "cVerbalPlural:cUngrammatical" = "Ungrammaticality * Verbal Attractor",
                    "cVerbalPlural:cAttractorPlural" = "Verbal Attractor * Plural Attractor",
                    "cVerbalPlural:cUngrammatical:cAttractorPlural" = "Verbal Attractor * Ungrammaticality * Plural Attractor")

    p_m_response_exp2 <- 
      create_model_coefs_plot( m_responses2, 
            plot_stats = T, map_names = contrast_names2_le,
            expand_right = 4.5, expand_top = 1.5, x_stat_adjust = .75,
            x_breaks = c(-3,-2,-1, 0, 1) ) + 
            xlab("Estimate (log-odds)")

    p_m_response_exp2 <- p_m_response_exp2 + annotate(x=-3, xend=1, y=0, yend=0, lwd=0.25, geom="segment")

    ggsave(filename = "./plots_le/m_exp2.jpeg", p_m_response_exp2, height = 2.5, width = 2.5*2)
}

@

### 2019-12-23 agremeent_draft_dec17/draft_dec17.tex
draft work
rnw done I guess

\documentclass[a4paper,man,natbib]{apa6}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

@@

\abstract{We report the results of two speeded acceptability judgment experiments in Turkish. We hypothesized an alternative explanation for agreement attraction effects in Turkish that is based on shallow processing. Our findings contradict our hypothesized form-driven processing strategy and support an account of agreement attraction based on the use of abstract linguistic features, rather than mere form.}
\input{settings.tex}
\begin{document}
\maketitle

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/exp1AvgResponse-1.png}
\caption{Percentage of ‘yes’ (acceptable) responses of Experiment 1 and \citet{LagoEtAl:2018}}
\label{fig:exp1AvgResponse}
\end{figure}

>>>>

\documentclass[doc,a4paper,man,natbib,floatsintext,noextraspace]{apa6}\usepackage[]{graphicx}\usepackage[]{color}
% maxwidth is the original width if it is less than linewidth
% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[singlespacing]{setspace}

@@

\abstract{We report the results of two speeded acceptability judgment experiments in Turkish. We hypothesized an alternative explanation for agreement attraction effects in Turkish that is based on shallow processing. Our findings contradict our hypothesized form-driven processing strategy and support an account of agreement attraction based on the use of abstract linguistic features, rather than mere form.}
\input{settings.tex}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

\maketitle

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}

{\centering \includegraphics[width=\maxwidth]{figure/exp1AvgResponse-1}

}

\caption{Percentage of \emph{yes} (acceptable) responses of Experiment 1 and \citet{LagoEtAl:2018}}\label{fig:exp1AvgResponse}
\end{figure}

\end{knitrout}
